---
title: "AI Skills Complementarity"
output: html_document
date: "2025-01-07"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Data set up

# Load libraries 
library(tidyverse)
library(DT) 

# Load data
table <- readxl::read_xlsx("List of Skills with Measures.xlsx") %>% 
  mutate(`Betweenness Centrality` = round(`Betweenness Centrality`, 2)) %>% 
  mutate(`Eigenvector Centrality` = round(`Eigenvector Centrality`, 2)) %>% 
  mutate(Complementarity = round(Complementarity, 2))
  
```

The table shows the skills demand in Italian AI-realted labour market. The results refer to the netwrok analysis performed on RStudio. The columns include:

* Skill: the label of a given skills included in the job vacancies
* Cluster: the number of the cluster which the skill belong to
* Demand: the number of job vacancies mentioning the skill
* Skill type: binary indicator for AI skill or ESCO skill
* Centrality measures: Betweenness Centrality, Degree Centrality, Eigenvector Centrality
* Complementarity: multiplication of Centrality measures

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Table Displays

DT::datatable(table, filter = "top", rownames = F, class = "cell-border stripe",
              extensions = 'Buttons', options = list(
                dom = 'Bfrtip', 
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))
              )
```
